Notebook of learning from ensemble labels

### 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
Add an argument of predict catalog to predict.py
Add another argument to predict

  ```
  git clone git@github.com:agroimpacts/pytorch_planet.git
  ```

@@

@@

  [TO BE CONTINUE]

>>>>

  ```
  git clone git@github.com:LLeiSong/hrlcm.git
  ```

@@

#### Prediction

```
python hrlcm/predict.py --args_path 'results/dl/resume/args.pkl' --checkpoint_file 'results/dl/resume/final.pth' --fname_predict 'results/north/dl_catalog_valid_full.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

@@

  Our experiments proved that architecture of DeepLab family has worse performance.
